
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
set.seed(1234)
```

Question 1
```{r}
#install.packages("topicmodels")
```


```{r}
# load libraries
library(textir) # to get the data
library(maptpx) # for the topics function
library(topicmodels)
```

```{r}
# load the congressional data
load("congress.RData")
```

```{r}
# Prepare the data for analysis
# Fitting k-means by first scaling while standardizing on frequency.
fs <- scale(as.matrix(congress109Counts / rowSums(congress109Counts)))
```


```{r}
# Deducing k-means for k = 5.
kmfs5 <- kmeans(fs,5)

# this output gives 5 groups and top 10 words in them
print(apply(kmfs5$centers,1,function(c) colnames(fs)[order(-c)[1:10]]))
```

```{r}
# the code below takes the dataset "fs" and we want 10 means. So "kmeans" will do this clustering.
kmfs10 <- kmeans(fs,10)

# this output gives 10 groups and top 10 words in them
print(apply(kmfs10$centers,1,function(c) colnames(fs)[order(-c)[1:10]]))
```

```{r}
# the code below takes the dataset "fs" and we want 15 means. So "kmeans" will do this clustering.
kmfs15 <- kmeans(fs,15)

# this output gives 15 groups and top 10 words in them
print(apply(kmfs15$centers,1,function(c) colnames(fs)[order(-c)[1:10]]))
```

```{r}
# the code below takes the dataset "fs" and we want 20 means. So "kmeans" will do this clustering.
kmfs20 <- kmeans(fs,20)

# this output gives 20 groups and top 10 words in them
print(apply(kmfs20$centers,1,function(c) colnames(fs)[order(-c)[1:10]]))
```

```{r}
# the code below takes the dataset "fs" and we want 25 means. So "kmeans" will do this clustering.
kmfs25 <- kmeans(fs,25)

# this output gives 25 groups and top 10 words in them
print(apply(kmfs25$centers,1,function(c) colnames(fs)[order(-c)[1:10]]))
```

Question 2
```{r}
# Elbow method
library(factoextra)
fviz_nbclust(fs, kmeans, method = "wss", k.max = 30)
#We can choose 24 based on the below plot
```

```{r}
# Create a function to deduce AIC / BIC
kic <- function(fit, rule=c("A","B", "CA")){
  df <- length(fit$centers) # K*dim
	n <- sum(fit$size)
	D <- fit$tot.withinss # deviance
	rule=match.arg(rule)
  if(rule=="CA")
		return(D + 2*df*n/(n-df-1))
	else if(rule == "A")
	  return(D + 2*df)
	else
		return(D + log(n)*df)
}
```


```{r}
# create a vector of clusters from k = 1 to k = 30
kfit <- lapply(1:30, function(k) kmeans(fs,k))
```

```{r}
# Next, we calculate aicc for all different clusters deduced from the k-fit
kaicc <- sapply(kfit, kic, "CA")

# Now we plot them:
plot(kaicc, xlab="K", ylab="AICc", bty="n", type="p", lwd=2,  pch = 21, col="red", bg = "red")
# AICc doesn'tmake sense in this case as the denominator becomes negative
```


```{r}
# Next, we calculate aic for all different clusters deduced from the k-fit
kaic <- sapply(kfit, kic, "A")

# Now we plot them:
plot(kaic, xlab="K", ylab="AIC", bty="n", type="p", lwd=2, pch = 21, col="blue", bg = "blue")
# Based on AIC, we can choose the value 28 for the number of clusters
```

#Question 3
```{r}
# Add libraries
library(textir)
library(maptpx)


x <- as.simple_triplet_matrix(congress109Counts)
```


```{r}
tpcs <- maptpx::topics(x, K=5*(1:5), verb=10)

summary(tpcs, n=10)
```


```{r}
rownames(tpcs$theta)[order(tpcs$theta[,1], decreasing=TRUE)[1:10]]
rownames(tpcs$theta)[order(tpcs$theta[,2], decreasing=TRUE)[1:10]]
```
# Question 3 - Answer
# Here the max Bayes factor chooses K=10 clusters (logBF = 77508.93) because this is the largest logBF.
# Interpretation of the topics:
# Topic 1 relates mostly to Asian Pacific Americans and African Americans.
# Topic 2 relates mostly to US Army veterans and their health care.
# Topic 3 relates to illegal immigration.
# Topic 4 relates largely to the Iraq's Oil for Food Program.
# Topic 5 relates to retirement policy and taxes related to retirement.
# Topic 6 relates to Tongass National Forest timber sales program.
# Topic 7 relates to a US judicial court and judge confirmations.
# Topic 8 relates to gun control and gun safety.
# Topic 9 relates to US trade policy, free trade, and the trade deficit.
# Topic 10 relates to stem cell research.

# Question 4
```{r}
library(glmnet)
```

```{r}
# Check first few rows
head(congress109Ideology)
```
```{r}
# pull out the data for "party" (make it numeric) and repshare, and put them into vectors
party <- as.numeric(congress109Ideology[,"party"])
repshare <- congress109Ideology[,"repshare"]

regtpcs.cv <- cv.glmnet(tpcs$omega, party)
```


```{r}
plot(regtpcs.cv)
```


```{r}
coef(regtpcs.cv)

rownames(tpcs$theta)[order(tpcs$theta[,6], decreasing=TRUE)[1:10]]
rownames(tpcs$theta)[order(tpcs$theta[,7], decreasing=TRUE)[1:10]]
rownames(tpcs$theta)[order(tpcs$theta[,10], decreasing=TRUE)[1:10]]
```
Topics 6, 7, and 10 have no coefficients. This indicates these topics do not increase or decrease the chance that a representative's constituents voted for Bush in 2004.  Topic 6 is mixed but mainly about climate and environment; 7 is about the judicial system; 10 is mostly about stem cell research. See the top 10 words in each of these topics below.

```{r}
regtpcs_repshare.cv <-cv.glmnet(tpcs$omega, repshare)
plot(regtpcs_repshare.cv)
     
coef(regtpcs_repshare.cv)
```
Representatives who discussed Topics 1, 2, 8, and 9 had more voters who did NOT vote for Bush in 2004. By contrast, those who spoke about 3 and 5 had a higher percentage of people who did vote for Bush.

```{r}
rownames(tpcs$theta)[order(tpcs$theta[,1], decreasing=TRUE)[1:10]]
rownames(tpcs$theta)[order(tpcs$theta[,5], decreasing=TRUE)[1:10]]
```


```{r}
# pull out the data for "party" (make it numeric) and repshare, and put them into vectors
x <- 100*congress109Counts/rowSums(congress109Counts)

regwords.cv <- cv.glmnet(x, party)
```

```{r}
plot(regwords.cv)
```


```{r}
regwords_repshare.cv <- cv.glmnet(x, repshare)
```

```{r}
plot(regwords_repshare.cv)
```
